```{r echo = FALSE, results = "hide"}
BRANCH <- Sys.getenv("APPVEYOR_REPO_BRANCH")
REF <- Sys.getenv("APPVEYOR_REPO_COMMIT")
MD5_iso <- tools::md5sum("R.iso")
size_mb_iso <- round(file.info("R.iso")$size / (2 ** 20), 1)
```
r-portable `r if (BRANCH != "master") sprintf("(branch: %s)", BRANCH)`
==========
[![Build status](https://ci.appveyor.com/api/projects/status/w016xch3qm00msde/branch/`r BRANCH`)](https://ci.appveyor.com/project/krlmlr/r-portable/branch/`r BRANCH`)

ISO images that contain everything necessary to build R packages.

Built by [AppVeyor](http://www.appveyor.com/). Uses [innounp](http://innounp.sourceforge.net/) and [.NET DiscUtils](http://discutils.codeplex.com/).

## Download

Most recent versions:

- [R.iso](https://rportable.blob.core.windows.net/r-portable/`r BRANCH`/R.iso) (`r size_mb_iso` MB, MD5 hash: `r MD5_iso`)
- [R.iso.gz](https://rportable.blob.core.windows.net/r-portable/`r BRANCH`/R.iso.gz) (much smaller)

Earlier versions are available through the [AppVeyor build history](https://ci.appveyor.com/project/krlmlr/r-portable/history) in the corresponding "ARTIFACTS" section of the individual builds.  ([Direct link](https://ci.appveyor.com/project/krlmlr/r-portable/build/artifacts) to the artifacts for the *latest* build.)

## Contents

```{r}
sessionInfo()
as.data.frame(installed.packages())[c("Version", "Priority")]
```
